Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-22 Articles/Article 1/main.tex
minor

We compute obstacle distances in task space with our unique matrix kernel method. Focusing on task space is beneficial as it provides a more direct and realistic representation of the environment, leading to better spatial awareness, quicker responsiveness, easier sensor integration, and more effective obstacle avoidance. Our method is particularly effective when integrating noisy sensor inputs like LIDAR or depth cameras for obstacle avoidance, \alert{as it robustly filters and interprets spatial data.}

>>>>

We compute obstacle distances in task space with our unique matrix kernel method. Focusing on task space is beneficial as it provides a more direct and realistic representation of the environment, leading to better spatial awareness, quicker responsiveness, easier sensor integration, and more effective obstacle avoidance. Our method is particularly effective when integrating noisy sensor inputs like LIDAR or depth cameras for obstacle avoidance, as it efficiently processes and utilizes this spatial information, even in the presence of noise, to accurately determine repulsive velocities.
